Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-05-22 paper.Rmd
updates paper

3.  improved transnational mobility through matching of the skills being delivered with European and Sectoral Frameworks for education, leading to individual workers being better enabled to demonstrate their skills to employers across Europe;

@@

Over the course of the project three groups of students worked on the project during the Smart Solutions Semester at Saxion University of Applied Sciences. This is an interdisciplinary semester in which students of at least three different study-programmes or disciplines work together on a complex problem/project (<https://www.saxion.edu/business-and-research/collaborate-with-saxion/smart-solutions>). The backgrounds of the various students were diverse: Applied Computer Science, Archaeology, Business Management Studies, Creative Business, Creative Media & Game Technologies, and ICT. The diverse groups of students contributed new ideas, developing educational material, testing the tutorials and developing a style for the website and other materials.

>>>>

3.  improved opportunities for archaeologists to work in other European countries (transnational mobility) through matching the skills being delivered with the European Commission's Digital Competence Framework for Citizens (2.2) and the sectoral Skills Passport for Archaeology, which will mean that it will be easier for individual workers to demonstrate their skills to employers across Europe;

@@

Over the course of the project three groups of students worked on the project during the Smart Solutions Semester at Saxion University of Applied Sciences. This is an interdisciplinary semester in which students of at least three different study-programmes or disciplines work together on a complex problem/project (<https://www.saxion.edu/business-and-research/collaborate-with-saxion/smart-solutions>). Within the semester students have to come up with new ideas or solutions to help a client with a wicked problem. The backgrounds of the various students we worked with were diverse: Applied Computer Science, Archaeology, Business Management Studies, Creative Business, Creative Media & Game Technologies, and ICT. The aim of involving interdisciplinary groups in the project was to involve students in current research projects, to enable them to learn new things and share their innovative ideas and solutions with us. The students groups were supplementary to the deliverables of the project, but their new ideas were benificial to the project. Their help during workshops was useful, but they also were engaged in developing educational material [@aalpoel2024], testing the tutorials, developing a style for the website [@jutte2024] and other materials.

### 2024-05-22 paper.tex
correction
updates paper

\title{Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists}
\author{true \and true \and true \and true \and true \and true \and true \and true \and true}
\date{April 25, 2024}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  a surge in professionals who can build, apply and critique archaeological simulation thus opening new research avenues for the discipline as a whole;
\item
  increased level of digital competence, specifically in advanced computer skills that are highly transferable to other industries. This includes technical skills such as programming but also ``soft'' skills related to computational thinking;
\item
  improved transnational mobility through matching of the skills being delivered with European and Sectoral Frameworks for education, leading to individual workers being better enabled to demonstrate their skills to employers across Europe;
\item
  increased opportunities for professional development by having access to professional training that can be incorporated into formal or non-formal/informal learning.
\end{enumerate}

@@

Over the course of the project three groups of students worked on the project during the Smart Solutions Semester at Saxion University of Applied Sciences. This is an interdisciplinary semester in which students of at least three different study-programmes or disciplines work together on a complex problem/project (\url{https://www.saxion.edu/business-and-research/collaborate-with-saxion/smart-solutions}). The backgrounds of the various students were diverse: Applied Computer Science, Archaeology, Business Management Studies, Creative Business, Creative Media \& Game Technologies, and ICT. The diverse groups of students contributed new ideas, developing educational material, testing the tutorials and developing a style for the website and other materials.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-councilofeurope2020}{}}%
Council of Europe. 2020. \emph{\href{http://www.coe.int/lang-cefr}{Common european framework of reference for languages: Learning, teaching, assessment. Companion volume}}. Strasbourg: Council of Europe Publishing.

>>>>

\title{Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists}
\author{true \and true \and true \and true \and true \and true \and true \and true \and true}
\date{May 22, 2024}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  a surge in professionals who can build, apply and critique archaeological simulation thus opening new research avenues for the discipline as a whole;
\item
  increased level of digital competence, specifically in advanced computer skills that are highly transferable to other industries. This includes technical skills such as programming but also ``soft'' skills related to computational thinking;
\item
  improved opportunities for archaeologists to work in other European countries (transnational mobility) through matching the skills being delivered with the European Commission's Digital Competence Framework for Citizens (2.2) and the sectoral Skills Passport for Archaeology, which will mean that it will be easier for individual workers to demonstrate their skills to employers across Europe;
\item
  increased opportunities for professional development by having access to professional training that can be incorporated into formal or non-formal/informal learning.
\end{enumerate}

@@

Over the course of the project three groups of students worked on the project during the Smart Solutions Semester at Saxion University of Applied Sciences. This is an interdisciplinary semester in which students of at least three different study-programmes or disciplines work together on a complex problem/project (\url{https://www.saxion.edu/business-and-research/collaborate-with-saxion/smart-solutions}). Within the semester students have to come up with new ideas or solutions to help a client with a wicked problem. The backgrounds of the various students we worked with were diverse: Applied Computer Science, Archaeology, Business Management Studies, Creative Business, Creative Media \& Game Technologies, and ICT. The aim of involving interdisciplinary groups in the project was to involve students in current research projects, to enable them to learn new things and share their innovative ideas and solutions with us. The students groups were supplementary to the deliverables of the project, but their new ideas were benificial to the project. Their help during workshops was useful, but they also were engaged in developing educational material (Aalpoel et al. 2024), testing the tutorials, developing a style for the website (Jutte et al. 2024) and other materials.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-aalpoel2024}{}}%
Aalpoel, R, Baan, E, Lucas, S, Mulder, J, Regts, S, Sijbrant, A, Jutte, A and Visser, R. 2024 \emph{Teaching material Agent-Based Modelling for Archaeologists (EN/NL)} DOI: https://doi.org/\href{https://doi.org/10.5281/zenodo.10950153}{10.5281/zenodo.10950153}.

\leavevmode\vadjust pre{\hypertarget{ref-councilofeurope2020}{}}%
Council of Europe. 2020. \emph{\href{http://www.coe.int/lang-cefr}{Common european framework of reference for languages: Learning, teaching, assessment. Companion volume}}. Strasbourg: Council of Europe Publishing.
